---
title: "Jam Markdown session"
author: "Nelda"
date: "4/12/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## What is R Markdown?
Watch this video https://vimeo.com/178485416 to start us off.<br>


_In summary_<br>
R Markdown is a file format for making dynamic documents with R.<br> Simple plain text file with 3 types of content <br>
1. Code Chuncks to run<br>
2. Texts to display<br>
3. Metadata to guide
<br>

Why is it Useful?<br>
* Generate reports of your work<br>
* Reproducibility
<br>

Building a report<br>
1. Use render function render("Jam Session.Rmd")<br>
2. Knit Button in the IDE<br>
<br>

Report Formats can be HTML, PDF, Word Document, SLideshows, dashboards, books, websites, intercative apps, etc <br>

##Getting Started<br>
Select File > TextFile<br>
Save with ext .Rmd<br>
OR<br>
select File > New File > R Markdown 

## Code Chunks to Run
- Using delimiters ```{r} ``` to write a code in R<br>
- Name your code chunck ```{r, name}```<br>
__Chunck Options__<br>
__eval__ = FALSE prevents code from being evaluated. (And obviously if the code is not run, no results will be generated). <br>
__include__ = FALSE runs the code, but doesn’t show the code or results in the final document. <br>
__echo__ = FALSE prevents code, but not the results from appearing in the finished file. <br>
__message__= FALSE or warning = FALSE prevents messages or warnings from appearing in the finished file.<br>
__results__ = 'hide' hides printed output; fig.show = 'hide' hides plots.<br>
__error__ = TRUE causes the render to continue even if code returns an error. <br>


## Slide with R Output

```{r women, echo = TRUE}
data(women)
str(women)
summary(women)
plot(women)
```

## Slide with Plot

```{r plots, echo=FALSE}
hist(women$height)
boxplot(women$weight)
```
## Inline R Code
<br>
The mean speed of women was `r mean(women$height)`.
<br>

#Assignment
